The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games

### 2025-05-07 Quarto/paper.qmd
Update Intro, Methods, WWA GUI Figure

Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure @fig:wwa-gui. The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.

@@

::: {.figure-caption #fig:wwa-gui}
**Figure 1.** GUI of Werewolf Arena simulation environment.
:::

>>>>

Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure 1. The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.

**Figure 1.** GUI of Werewolf Arena simulation environment.

@@
